---
title: "Analysis of FrogID Data"
subtitle: "Proposal"
author: 
  - name: "Kayla Mac"
    affiliations:
      - name: "School of Information, University of Arizona"
description: "Using data from an Australian application, FrogID, two questions will be answered: how does frog call frequency across seasons and how does taxonomic diversity differ across Australia."
format:
  html:
    code-tools: true
    code-overflow: wrap
    code-line-numbers: true
    embed-resources: true
editor: visual
code-annotations: hover
execute:
  warning: false
  echo: false
  message: false
---

```{r}
#| label: load-pkgs
#| message: false
library(tidyverse)
```

## Dataset

```{r}
#| label: load-dataset
#| message: false
# FrogID data
frogID_data <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2025/2025-09-02/frogID_data.csv')

# Frog name data
frog_names <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2025/2025-09-02/frog_names.csv')
```

Data set: Australian frogs

This data set contains 2023 data from the app, FrogID. FrogID is an Australian app that allows people to submit frog calls and museum experts can identify the type of frog. Along with the FrogID data, there is an additional table that includes their names.

The frogID dataset contains `r ncol(frogID_data)` columns by `r nrow(frogID_data)` rows. The dataset contains the following information:

-   `occurenceID`, `eventID`, `decimalLatitude`, `decimalLongitude`, `scientificName`, `eventDate`, `eventTime`, `timeZone`, `coordinateUncertaintyInMeters`, `recordedBy`, `stateProvince`

The frog names dataset contains `r ncol(frog_names)` columns and `r nrow(frog_names)` rows. The dataset contains the following information:

-   `subfamily`, `tribe`, `scientificName`, `commonName`, `secondary_commonNames`

## Motivation

I majored in biology in undergraduate and really enjoyed the ecology electives I took. Additionally, I love watching nature and animal documentaries so choosing a frog data set seemed fitting and piqued my interest.

## Questions

1.  What is the spatiotemporal distribution of Australian frog occurrences, and how does call frequency change across seasons?
2.  Do geographic hotspots with the highest density of frog occurrences also exhibit the highest levels of taxonomic diversity?

## Analysis plan

**Question 1:** What is the spatiotemporal distribution of Australian frog occurrences, and how does call frequency change across seasons?

-   **Spatiotemporal:** in relation to both space and time.

    -   For example, how does Australian frog occurrences change with season (time) and location in Australia (space).

<!-- -->

-   Due to Australia being in the southern hemisphere, their months for seasons are not the same as North America -- Use `eventDate` to determine month and then season.

    -   Fall: March, April, May

    -   Winter: June, July, August

    -   Spring: September, October, November

    -   Summer: December, January, February

-   Make a map of Australia

    -   Use `decimalLatitude` and `decimalLongitude` variables to plot where each of these calls are taking place in Australia. Additionally, map out the states using the `stateProvince` variable.

        -   Map the states and where each frog call is occurring on the map.

-   Make four different plots for each season -- in each plot is a bar chart showing how the number of calls differ across seasons and provinces.

-   Data wrangling:

    -   Variables used: `eventDate`, `decimalLatitude`, `decimalLongitude`, and `stateProvince`

    -   Variables need to create: `season`

    -   Approach: using the month in `eventDate`, assign the correct season. Using the package `ozmaps`, I can assign the Australian states and then plot where the frog calls are occurring.

**Question 2:** Do geographic areas with the highest density of frog occurrences also exhibit the highest levels of taxonomic diversity?

-   **Taxonomy:** classification of organisms --- different species will determine diversity.

<!-- -->

-   Based off the previous data, we will be able to determine geographically where the most frog occurrences.
-   Determine what is considered the equatorial, tropical, subtropical, desert, grassland, temperate.
-   To determine taxonomic diversity, use the `subfamily` or `tribe`. A tribe is part of a subfamily. A subfamily may be too broad for the frog species and not show the true diversity. If that is so, I will use `tribe` to showcase the diversity.
    -   Plot the number of different subfamilies/tribes per geographical region.
    -   Graph another plot that is a stacked bar chart with the different subfamilies or tribes.
-   Data wrangling:
    -   Variables used: `subfamily`, `tribe`, `decimalLatitude`, `decimalLongitude`
    -   Variables need to create: `climate_zone`
    -   External data:
        -   Australian Bureau of Meteorology (geographic areas): [Australian Bureau of Meteorology](https://www.bom.gov.au/climate/maps/averages/climate-classification/?maptype=koppen_major_AGCDv2_&period=1991-2020)
        -   Australian states: [Ozmaps](https://github.com/mdsumner/ozmaps/)
    -   Join the geographical regions by location to the frogID data frame using the external data from package `Ozmaps` and the climate classification by the Australian Bureau of Meteorology.
    -   Approach: Make a map of Australia defined by the different climate zones equatorial, tropical, subtropical, desert, grassland, temperate. Create a bar chart for the number of species per climate zone (x-axis: region; y-axis: number of different subfamilies/tribes) and state.

## Weekly project plan table

| **Task Name**                       | **Status**  | **Due** | **Priority** | **Summary**                            |
|---------------|---------------|---------------|---------------|---------------|
| Peer review                         | Complete    | 6/12/26 | High         | Reach out to peer reviewers            |
| Make adjustments after peer reviews | Complete    | 6/12/26 | Moderate     | Waiting for 2nd peer review            |
| Data wrangling                      | Complete    | 6/17/26 | High         | Need to make new variables for seasons |
| Explore Ozmaps                      | Complete    | 6/17/26 | Moderate     | See what the Ozmaps package includes   |
| Question 1                          | Complete    | 6/28/26 | High         | Data wrangle and plots                 |
| Question 2                          | In progress | 6/28/26 | High         | Data wrangle and plots                 |
| Write-up                            | In progress | 7/3/26  | High         | Dataset overview & workflow            |
| Presentation                        | In progress | 7/3/26  | High         | Slides and video presentaion           |
| Final project due                   | In progress | 7/3/26  | High         | Upload to Github                       |
